---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

  [![R-CMD-check](https://github.com/BrydenFrancesca/strangeRthings/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/BrydenFrancesca/strangeRthings/actions/workflows/R-CMD-check.yaml)


The strangeRthings package aims to provide tidy format transcripts of [Stranger Things](https://en.wikipedia.org/wiki/Stranger_Things) episodes as an R package.

The data originates from [Subslikescript](https://subslikescript.com/series/Stranger_Things-4574334) which contains the transcripts of all episodes in text format. This package presents the transcripts in a tidy tibble format, making them easy to load and use in R.

## Installation


Install the strangeRthings package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("BrydenFrancesca/strangeRthings")
```

## Example

The package comes with a single dataset (`stranger_text`), which is a tibble containing all the utterances in the
show.

```{r example}
library(strangeRthings)

dplyr::glimpse(stranger_text)
```

All the utterances are broken down by `season`, `episode`, and `utterance` which allows for very detailed analysis. Please note that the `character` will be denoted `"Scene Directions"` to show scene directions, or otherwise non-spoken descriptions. Currently `character` descriptions are only available when given in the transcript, so many utterances are 
unassigned.



